New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-03-12 main.tex
Use default 'article' class
Rewrite the abstract to highlight the impact of this research

\documentclass{acm_proc_article-sp}

@@

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}

@@

\title{Eye-tracking measures for Anthropomorphism in Human Robot Interaction}

\numberofauthors{1} %  
\author{
\alignauthor Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
    \affaddr{CHILI Lab, École Polytechnique Fédérale de Lausanne}\\
       \email{firstname.lastname@epfl.ch}
}

@@

We present a study that investigates the relation between anthropomorphism and
gaze patterns of the observers. Anthropomorphism usually refers to attributing
human-like characteristics by a human to a non-human agent/entity; in this
study, the non-human entity is a robot.

We hypothesize that while observing a human-robot interaction in a particular
setting, the observer develops an anthropomorphic behavior for the robot.
Moreover, the resulting anthropomorphism can be correlated with the gaze
patterns of the observer as well as with the recorded response of the
participants about their experience of the interaction (in the form of a
questionnaire), both before and after the experiment. We try to seek the answer
to the question whether anthropomorphism goes beyond the shape and body
features, and we indeed observe that just by the use of audio commands of
different cognitive levels, anthropomorphic attitude gets affected. We obtain
two other useful results. First, eye tracking serves to be an effective way for
measuring anthropomorphism. Second, in our study, the standard anthropomorphism
tests are also validated such as, a person who can anthropomorphize more, in
general, responds to a human scene and a robot scene in a similar manner.

We observe a significant increase in the gaze fixations over the actor's head
for a high cognitive scene compared to a low cognitive scene. We also achieve
the result that the high cognitive interaction scenarios are capable of inducing
anthropomorphic behavior more than the low cognitive scenarios.

@@

\keywords{anthropomorphism, eye tracking, gaze patterns, robot}

>>>>

%\documentclass{acm_proc_article-sp}
\documentclass[a4,twocolumn,10pt]{article}

@@

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}

\usepackage[draft,nomargin,footnote]{fixme}

@@

\title{New Insights on the Role of Context in the Perception of a Human-like Robot}

\author{
Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
CHILI Lab, École Polytechnique Fédérale de Lausanne\\
\url{firstname.lastname@epfl.ch}
}

@@

What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot, as well as the design of the behaviours, certainly play a key
role. This paper however evidences another mechanism at play, more subtle and partially
unconscious: the \emph{cognitive context}\fxwarning{cognitive context, really?}
of the interaction.

To study this effect, we propose an original methodology based on eye-tracking
and a serie of stimuli that are visually identical and yet elicit different
assumptions regarding the cognitive capabilities of the robot. We then correlate
the gaze patterns with established questionnaires that assess anthropomorphic
attributions.

\begin{inparaenum}[\itshape a\upshape)]
As a result, we show that \item gaze patterns correlate with post-hoc anthropomorphic
attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
metric of anthropomorphism, \item fixations on the robot's head are a good
predictor of anthropomorphic attributions, \item simple context priming is sufficient
to elicit significantly different anthropomorphic attributions.
\end{inparaenum}

This last item has noteworthy implications regarding the design of human-like human-robot
interactions, and we propose to discuss them at the end of the article.

%We present a study that investigates the relation between anthropomorphism and
%gaze patterns of the observers. Anthropomorphism usually refers to attributing
%human-like characteristics by a human to a non-human agent/entity; in this
%study, the non-human entity is a robot. 
%
%We hypothesize that while observing a human-robot interaction in a particular
%setting, the observer develops an anthropomorphic behavior for the robot.
%Moreover, the resulting anthropomorphism can be correlated with the gaze
%patterns of the observer as well as with the recorded response of the
%participants about their experience of the interaction (in the form of a
%questionnaire), both before and after the experiment. We try to seek the answer
%to the question whether anthropomorphism goes beyond the shape and body
%features, and we indeed observe that just by the use of audio commands of
%different cognitive levels, anthropomorphic attitude gets affected. We obtain
%two other useful results. First, eye tracking serves to be an effective way for
%measuring anthropomorphism. Second, in our study, the standard anthropomorphism
%tests are also validated such as, a person who can anthropomorphize more, in
%general, responds to a human scene and a robot scene in a similar manner.
%
%We observe a significant increase in the gaze fixations over the actor's head
%for a high cognitive scene compared to a low cognitive scene. We also achieve
%the result that the high cognitive interaction scenarios are capable of inducing
%anthropomorphic behavior more than the low cognitive scenarios.

@@

%\keywords{anthropomorphism, eye tracking, gaze patterns, robot}
